Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-05 docs/evol.tex
correct OrderedDict init and version history

>>>>

The relation between bugs and time can be traced from the number of
bugs per category in each project version. We can then calculate the
correlations between the defects count and the ordinal version number
across all projects to see if bigger versions relate to higher or
lower defect counts. The results are shown in
Table~\ref{tbl:bugsperversion}. Although the tendency is for
defect counts to increase, this tendency is extremely slight.
\begin{table}
    \centering
    \caption{Correlations between Version and Defects Count}
    \label{tbl:bugsperversion}
    \input{bugsperversion.tex}
\end{table}
